---
title: "Tutorial 9"
author: "XXXX"
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: dinat
subtitle: Team name
header-includes:
- \usepackage{titling}
- \usepackage{float}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---

\clearpage

# Section 1



\clearpage

# Section 2

```{r load-packages}
library(tidyverse)
library(kableExtra)
library(bookdown)
library(ggplot2)
```

```{r read-in-data}
crime_data <- read_csv("Data/Data_Tables_Criminal_Incidents_Visualisation_Year_Ending_December_2019.csv")
```

```{r clean-data}
property_and_deception_offences <- crime_data %>%
  rename("Offence_Division" = "Offence Division") %>%
  filter(Offence_Division == "B Property and deception offences") %>%
  select(Year, "Incidents Recorded") %>%
  group_by(Year) %>%
  rename("Incidents_Recorded" = "Incidents Recorded") %>%
  summarise(n = sum(Incidents_Recorded)) %>%
  rename(Incidents_Recorded = n)
```

```{r prop-dep-plot, fig.cap = "Property and deception offences in Victoria by year"}
property_and_deception_offences %>%
  ggplot(aes(x = Year, 
             y = as.numeric(Incidents_Recorded))) + 
  geom_bar(stat="identity") +
  labs(y = "Incidents Recorded")
```

```{r prop-dep-tab}
property_and_deception_offences %>%
  kable(caption = "Property and deception offences in Victoria by year") %>%
  kable_styling(bootstrap_options = "striped")
```

## Discussion

From Figure \@ref(fig:prop-dep-plot) and Table \@ref(tab:prop-dep-tab), it can be seen that the level of Property and deception offences in Victoria has not changed significantly over the 2010-2019 period; it has stayed relatively stable. This is predicted in the paper by. The plot was produced using the package ggplot2 by @ggplot2.  

\clearpage

# Section 3


\clearpage

# Section 4


\clearpage

# Citation examples

[More styles for natbib here](https://www.overleaf.com/learn/latex/Natbib_bibliography_styles)


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2
